Research log

### 2025-10-09 docs/preregisteredMethodsAndResults.Rmd
model fits merged into one file, saving intermediate data automatically, and beautifying some parts of the paper

```{r global_options, include=FALSE}
set.seed(42)
knitr::opts_chunk$set(fig.crop = F, fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=T, 
                      message=F, sanitize = T, 
                      fig.width = 10, fig.height = 5)
```

@@

groundhog.library(c(
  'png',
  'grid',
  'ggplot2',
  'svglite',
  'xtable',
  'papaja',
  'tidyverse',
  'broom',
  'cowplot',
  'MESS', # for AUCs
  'lsr', # for effect sizes
  'pwr', # for power calculations
  'brms', # for mixed effects modeling
  'BayesFactor', # for Bayesian t test
  'jsonlite', # parsing data from sort_trial
  'caret', #for cross validation
  'ggrepel' #for word scatterplots
), '2022-12-01')

@@

# E4.click_log <- data.frame(matrix(ncol=11,nrow=0,
#                                dimnames=list(NULL,
#                                              c("subj_id",
#                                               "test_part",
#                                               "word",
#                                               "category",
#                                               "num_clicks",
#                                               "num_misses",
#                                               "letter",
#                                               "hit",
#                                               "t",
#                                               "click_number",
#                                               "genuine_first"))))

# for (row in 1:nrow(E4.click_df)) {
# 
#     subject_click_log <- data.frame(fromJSON(E4.click_df[row, ]$click_log)) %>%
#     mutate(
#       letter = lead(letter,1),
#       t = lead(t,1),
#       hit = lead(hit,1),
#       click_number = 1:n(),
#       subj_id = E4.click_df[row, ]$subj_id,
#       test_part = E4.click_df[row, ]$test_part,
#       word = E4.click_df[row, ]$word,
#       category = E4.click_df[row, ]$category,
#       num_clicks = E4.click_df[row, ]$num_clicks,
#       num_misses = E4.click_df[row, ]$num_misses,
#       genuine_first = E4.click_df[row, ]$genuine_first
#     )%>%
#       filter(click_number<=num_clicks)
# 
#     E4.click_log <- rbind(E4.click_log, subject_click_log);
# }

# E4.click_log <- E4.click_log %>%
#   relocate(subj_id, .before = letter) %>%
#   relocate(genuine_first, .before = letter) %>%
#   relocate(test_part, .before=letter) %>%
#   relocate(word, .before=letter) %>%
#   relocate(category, .before=letter) %>%
#   relocate(click_number, .before=letter) %>%
#   group_by(subj_id,test_part,word) %>%
#   mutate(RT=t-lag(t,default=0)) %>%
#   group_by(subj_id,word) %>%
#   rowwise()

# save(..experiments/Hangman2/data/E4.click_log, file='E4.click_log.RData')

load('..experiments/Hangman2/data/E4.click_log.RData')
```

@@

>>>>

```{r global_options, include=FALSE}
set.seed(42)
knitr::opts_chunk$set(fig.crop = F, fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=T, 
                      message=F, sanitize = T, 
                      fig.width = 10, fig.height = 5,
                      dev = "ragg_png", dpi = 300, fig.width = 6, fig.height = 4)

@@

groundhog.library(c(
  'png',
  'grid',
  'ggplot2',
  'svglite',
  'xtable',
  'papaja',
  'tidyverse',
  'broom',
  'cowplot',
  'MESS', # for AUCs
  'lsr', # for effect sizes
  'pwr', # for power calculations
  'brms', # for mixed effects modeling
  'BayesFactor', # for Bayesian t test
  'jsonlite', # parsing data from sort_trial
  'caret', #for cross validation
  'ggrepel', #for word scatterplots
  'ragg' # for png
), '2022-12-01')

@@

# E4.click_log <- data.frame(matrix(ncol=11,nrow=0,
#                                dimnames=list(NULL,
#                                              c("subj_id",
#                                               "test_part",
#                                               "word",
#                                               "category",
#                                               "num_clicks",
#                                               "num_misses",
#                                               "letter",
#                                               "hit",
#                                               "t",
#                                               "click_number",
#                                               "genuine_first"))))
# 
# 
# for (row in 1:nrow(E4.click_df)) {
# 
#     subject_click_log <- data.frame(fromJSON(E4.click_df[row, ]$click_log)) %>%
#     mutate(
#       letter = lead(letter,1),
#       t = lead(t,1),
#       hit = lead(hit,1),
#       click_number = 1:n(),
#       subj_id = E4.click_df[row, ]$subj_id,
#       test_part = E4.click_df[row, ]$test_part,
#       word = E4.click_df[row, ]$word,
#       category = E4.click_df[row, ]$category,
#       num_clicks = E4.click_df[row, ]$num_clicks,
#       num_misses = E4.click_df[row, ]$num_misses,
#       genuine_first = E4.click_df[row, ]$genuine_first
#     )%>%
#       filter(click_number<=num_clicks)
# 
#     E4.click_log <- rbind(E4.click_log, subject_click_log);
# }
# 
# 
# E4.click_log <- E4.click_log %>%
#   relocate(subj_id, .before = letter) %>%
#   relocate(genuine_first, .before = letter) %>%
#   relocate(test_part, .before=letter) %>%
#   relocate(word, .before=letter) %>%
#   relocate(category, .before=letter) %>%
#   relocate(click_number, .before=letter) %>%
#   group_by(subj_id,test_part,word) %>%
#   mutate(RT=t-lag(t,default=0)) %>%
#   group_by(subj_id,word) %>%
#   rowwise()

load('../experiments/Hangman2/data/E4.click_log.RData')

@@

```{r save data, echo-FALSE}

save.image(file = file.path(getwd(), "prereg_results.RData"))
